---
title: "Linear Regression on Advertising Data"
output: html_notebook
author: Shiva Kumar Pendem
---


```{r Importing_libs}
library(ggplot2)
library(car)
library(vctrs)
library(plotly)
```

------------------------------------------------------------------------

## Task 1: Load and visualize the data

### Loading the Data and getting summary

```{r Loadingdata}

advertising_data <- read.csv("Advertising.csv", colClasses = c("NULL", NA,NA,NA,NA))

head(advertising_data)

summary(advertising_data)



```

------------------------------------------------------------------------

------------------------------------------------------------------------

## Task 2: Simple linear regression

```{r Plotting}


par(mfrow=c(1,3))


plot(advertising_data$TV, advertising_data$Sales, main="TV vs Sales", xlab="TV", ylab="Sales")
plot(advertising_data$Radio, advertising_data$Sales, main="Radio vs Sales", xlab="Radio", ylab="Sales")
plot(advertising_data$Newspaper, advertising_data$Sales, main="Newspaper vs Sales", xlab="Newspaper", ylab="Sales")


par(mfrow=c(1,1))
```

```{r Multimodel}
multi_model <- lm(Sales ~ TV + Radio + Newspaper, data = advertising_data)
summary(multi_model)

```

### Plotting with Regression Line

```{r Plotting with Regression line}
par(mfrow=c(1,3))

# TV vs Sales
plot(advertising_data$TV, advertising_data$Sales, main="TV vs Sales", xlab="TV", ylab="Sales")
model_tv <- lm(Sales ~ TV, data=advertising_data)
abline(model_tv, col="red")

# Radio vs Sales
plot(advertising_data$Radio, advertising_data$Sales, main="Radio vs Sales", xlab="Radio", ylab="Sales")
model_radio <- lm(Sales ~ Radio, data=advertising_data)
abline(model_radio, col="red")

# Newspaper vs Sales
plot(advertising_data$Newspaper, advertising_data$Sales, main="Newspaper vs Sales", xlab="Newspaper", ylab="Sales")
model_newspaper <- lm(Sales ~ Newspaper, data=advertising_data)
abline(model_newspaper, col="red")

par(mfrow=c(1,1))
```

### Based on the the results:

The coefficients of TV, Radio and Newspaper are 0.045, 0.188, -0.001 respectively.

TV and Radio contribute to sales because the coeff is significant, which we can't say for Newspaper.

Based on the t-values:

There's a strong positive relationship between sales and the advertising budgets for both TV and Radio, as indicated by their large positive t-values. The Newspaper advertising budget doesn't show a statistically significant relationship with sales, given its t-value close to 0. Thus, while TV and Radio budgets have significant positive relationships with sales, the Newspaper budget doesn't seem to have a meaningful impact on sales. \*\*\* \\

## Question 3: Multiple Linear Regression

```{r}
# install.packages(c("car", "rgl"))

summary(multi_model)
```

### Revisiting the results:

Again, Looking at the Coefficients of TV and radio tells us the they contribute more to the sales because of their corresponding slopes is more when compared to Newspaper's slope.

```{r Newspaper_VS_Sales}
plot(advertising_data$Newspaper, advertising_data$Sales, main="Newspaper vs Sales", xlab="Newspaper", ylab="Sales")
model_newspaper <- lm(Sales ~ Newspaper, data=advertising_data)
abline(model_newspaper, col="red")
summary(model_newspaper)

```
### Multiple and Simple Regression for Newspaper regressor.

When performing the simple regression on newspaper alone, it gives us the coeff of 0.0546. Indicating a good relationship

The p-value is 0.0015 (When newspaper is isolated)

But when we do multiple linear regression the slope of newspaper is -0.001037 and the p-value is 0.86. Indicating, that it doesn't have much affect on sales.

```{r}
correlation_matrix <- cor(advertising_data[, c('Sales','TV', 'Radio', 'Newspaper')])
print(correlation_matrix)
```

Looking at the correlation between Newspaper and other regressor tells us it has weak correlation.

```{r Rsquared for all }
r2 = summary(multi_model)$r.squared
print(paste("R-squared value is:", r2))


```

The R-Squared Value is 0.89

```{r 3D}

scatter3d(Sales ~ TV + Radio, data = advertising_data)
# scatter3d(Sales ~ TV + Newspaper, data = advertising_data)
# scatter3d(Sales ~ Newspaper + Radio, data = advertising_data)

```

------------------------------------------------------------------------

## Task 4: Models with interaction terms

```{r TV&Radio_Interaction}
synergy_model <- lm(Sales ~ TV + Radio + Newspaper + TV*Radio, data = advertising_data)
summary(synergy_model)

```

### Synergy between TV & Radio:

After including the TV x Radio term in the multi-linear regression. It gives the coefficient of <TV:Radio> to be 0.001087, although the slope in minimum, the relationship of <TV:Radio> can't be ignored because the corresponding significance code is \*\*\* and the p-value is less and almost as TV's p-value.

```{r testing}
#testing all possible variations of  interactions
testing_model <- lm(Sales ~ TV + Radio + Newspaper + TV*Radio + Radio*Newspaper + Newspaper*TV, data = advertising_data)
summary(testing_model)

```

### Testing all possible variations of interactions.

When I included all possible variations of interactions between regressor , it also suggested me that <TV:Newspaper> interaction is also significant based on the significance code '\**'. It gave a R-squared value of 0.96* \*\*.

### Task 5: Optimize Sales

```{r TVandRadio}
finalmodel <- lm(Sales ~ TV + Radio  + TV*Radio , data = advertising_data)
summary(finalmodel)

```

```{r Viz}
max(advertising_data$Sales)

print(paste('The maximum sales of existing data is', max(advertising_data$Sales), 'units'))

```

```{r ConfidenceInterval}

confint(finalmodel, 'TV', level=0.95)
confint(finalmodel, 'Radio', level=0.95)
```

Above is the calculation for Confidence interval for TV and Radio features.

```{r PredictModel}

predict(finalmodel, data.frame('TV'=145.534, 'Radio' = 154.465))

```



